Apparent preferences for cognitive effort fade when multiple forms of effort and delay are interleaved in a foraging environment

### 2020-03-26 Cost_manuscript.Rmd
3/4 of results drafted, plus all methods

@@

@@

  In short, participants faced with different behavioral costs were tasked with deciding their preferred strategy to maximize rewards in fully-disclosed foraging environments of variable richness.

@@

  where R, H, and P are the reward, handling time, and acceptance probability of trial i, respectively, and T is the travel times. This gives the total reward per second attainable in each block as a function of the lowest amount accepted (i.e. acceptance threshold). Figure X shows possible earnings for each choice strategy, as well as the lowest amount participants should accept in order to maximize their rewards (circled dots). For example, a participant in a 10 s handling block should accept 8-cent and 20-cent rewards (and reject 4-cent rewards) to maximize their reward rate. Significant deviations from the optimal strategy can be understood as reflecting changes in subjective OC. Beyond comparing among cost types, this approach allowed us to test if certain demands boosted the value of offers (i.e. over-accepting low offers).

@@

	Our foraging task was configured such that over and under accepting were detrimental to total earnings. To confirm this, we fit a general linear model with constant, linear, and quadratic terms to estimate the correspondence between proportion accepted (independent variable) and total earnings (dependent variable). A significant quadratic coefficient thus would signal that the task statistics operated as expected. Next, to determine the optimality of each group’s decisions, performed two-sided one-sample t-tests to see if the proportion of acceptances for each time/reward combination was significantly different from the optimal rate (see Operationalization of Cost above). This resulted in 36 independent tests (3 rewards amounts, 3 handling/travel time combinations, and 4 groups), so we corrected for multiple comparisons using False Discovery Rate (FDR) CHANGE TO COST3 APPROACH.
  Next we compared preferences among cost conditions. We first performed a one-way ANOVA on the proportion of trials accepted using group as a factor. We then compared the proportion completed among all 4 groups using non-parametric permutation contrasts (6 tests). The same approach was used for total earnings. This gave us an initial glimpse on the potential differences in cost among conditions. In order to further look at the effect of delay, work, and rewards, we will perform a repeated measures ANOVA on the proportion completed for each combination of factors. Reward and handling time will be within-subject factors, and condition a between-subjects factor. In support of hypotheses 4.1. and 4.2., we anticipate significant main effects of handling time, reward, and cost condition, but no interactions (MAYBE REMOVE, EXPLAINING WHY IT’S REDUNDANT). We computed the probability of accepting a trial with a mixed-effects logistic regression. Based on the task structure and our main question, our a priori model of interest included cost condition, handling time, and reward amount as fixed main effects, and subject ID as a random effect. Cost condition was modeled with three categorical terms, with the fourth condition as the reference condition. We ran three versions of the model with different reference conditions, in order to test all pairwise differences among the four cost conditions. As preregistered, we anticipated significant main effects (coefficients different than zero) of handling time, reward, and cost condition. We hypothesize that the differences among cost conditions will follow the pattern described in 4.2. We then examined whether this a priori model outperformed both simpler and more complex models. We used both Akaike’s Information Criterion (AIC) and Bayesian Information Criterion (BIC) to determine the model that minimized the negative log-likelihood while penalizing the addition of parameters. The regression with each combination of predictors was fitted in the following order: 1) intercept only; 2) cost type only; 3) handling time only; 4) reward only; 5) condition, handling, and reward main effects (a priori model); 6) adding a handling-by-reward interaction; and 7) adding all three possible two-way interactions. We predicted that model 5 would have the lowest AIC.

@@

  To compare acceptance rates among cost conditions, we first computed the probability of accepting a trial with a mixed-effects logistic regression. The model included cost condition and reward amount as fixed main effects, and subject ID as a random effect (does this make sense? It’s specified just like the previous one). Cost condition was modeled with three categorical terms, with the fourth condition as the reference condition (two effort conditions, and two delay conditions corresponding to each effort type). We ran three versions of the model with different reference conditions, in order to test all relevant pairwise differences among the four cost conditions. Next, we compared this model to both simpler and more complex models using Akaike’s Information Criterion (AIC) and Bayesian Information Criterion (BIC). We added varied model complexity in the following order: 1) intercept only; 2) condition only; 3) reward only; 4) condition and reward main effects (base model); and 5) adding a two-way interaction. We predicted that model 4 would have the last considerable decrease in the negative log-likelihood.

@@

``` {r BTW: 16.1.1., fig.align="center", fig.width = 4, fig.height = 4, echo = FALSE}
# filter out errors and compute R + H logistic per subject, then get coefficients
logisRH <- dataBtw %>%
  filter(Choice < 2) %>%
  plyr::dlply("SubjID", identity) %>%
  lapply(function(data) {glm(Choice ~ Handling + Offer, data = data, family = "binomial")}) %>%
  sapply(coefficients)

@@

# Plot coeffs
temp <- melt(logisRH[c("Handling", "Offer"), ])
qplot(data = temp, x = Var1, y = value, geom = "boxplot") + 
  labs(x = "", y = "Coefficients") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  theme(legend.position = c(0.9, 0.7),
       panel.grid.major = element_blank(), 
       panel.grid.minor = element_blank(), 
       panel.background = element_blank(), 
       axis.line = element_line(colour = "black"),
       text = element_text(size = 16))
```

``` {r BTW: 16.1.2., echo = FALSE, include = FALSE}
# add an AR regressor to track recent quits
logisRHAR <- dataBtw %>%
              filter(Choice < 2) %>%
              group_by(SubjID) %>%
              mutate(AR = seqQuits(Choice)) %>%
              plyr::dlply("SubjID", identity) %>%
              lapply(function(data) {suppressWarnings(glm(Choice ~ Handling + Offer + AR, data = data, family = "binomial"))})

@@

  Before comparing acceptance rates among cost conditions, we determined whether participants integrated the rewarding statistics of the experimental environment. We first confirmed that increasing handling times and reward amounts produced the expected reduction and increase in acceptance probabilities, respectively. Logistic regression coefficients for handling time were significantly lower than 0 across participants (mean $\beta$ = `r mean(rankAR, na.rm = T)`, SE = `r coeffRH_se[2]`; Wilcoxon test: V = `r rankHand$statistic`, p `r ifelse(rankHand$p.value < 0.001, "< 0.001", paste("=", round(rankHand$p.value, digits = 2)))`), whereas increasing the reward amount resulted in higher probabilities (mean $\beta$ = `r coeffRH_mean[1]`, SE = `r coeffRH_se[1]`; Wilcoxon test: V = `r rankOffer$statistic`, p `r ifelse(rankOffer$p.value < 0.001, "< 0.001", paste("=", round(rankHand$p.value, digits = 2)))`). We next examined whether choices could also have been affected by recent choice history (i.e. if too many sequential quits promoted acceptances regardless of reward amount) by adding a regressor to the model that tracked the number of quits preceding a trial. This auto-regressive coefficient was not significantly different than 0 across the whole group (mean $\beta$ = `r coeffRHAR_mean[3]`, SE = `r coeffRHAR_se[3]`; Wilcoxon test: V = `r rankRHAR$statistic`, p `r ifelse(rankRHAR$p.value < 0.001, "< 0.001", paste("=", round(rankRHAR$p.value, digits = 2)))`). Further, the 95% confidence interval (CI) of these coefficients contained 0 in `r round((sum(AR_CIs) / nSubjs_btw) * 100)`% of our participants.

### BTW: 16.1.3.

*A general linear model with constant, linear, and quadratic terms will be used to estimate the correspondence between proportion accepted (independent variable) and total earnings (dependent variable). No other covariates will be used, as this analysis is to confirm that over and under accepting are detrimental to total earnings. The quadratic term will be defined as the squared deviation from the optimal overall acceptance rate.*

@@

# plot
(earnFitplot <- ggplot(data = temp, aes(pComplete, Earnings)) + 
         scale_color_manual(values = colsBtw) + 
         geom_point(aes(fill = Cost), pch = 21, color = "black", size = 3, show.legend = T) + 
         stat_smooth(aes(y = Earnings), method = "lm", formula = y ~ x + I(x^2), color = "grey30") +
         labs(x = "Proportion Completed", y = "Total Earnings (dollars)") +
         scale_fill_manual(values = colsBtw) +
         theme(panel.grid.major = element_blank(), 
           panel.grid.minor = element_blank(), 
           panel.background = element_blank(), 
           axis.line = element_line(colour = "black"),
           text = element_text(size = 16)))

@@

The figure shows that participants that over and unceraccepted earned less money overall, as predicted. This is supported by a significant quadratic term from the linear model (F = `r round(summary(lmEarn)$fstatistic[1], digits = 2)`, Beta = `r summary(lmEarn)$coefficients[3,1]`, SE = `r round(summary(lmEarn)$coefficients[3,2], digits = 2)`, R-squared = `r round(summary(lmEarn)$r.squared, digits = 2)`; black line shows the fit). The following table shows all the results from the model.

``` {r BTW: 16.1.3. Earnings table, echo=FALSE,fig.align="center",fig.width=9,fig.height=5}
# Summary table for the linear model
panderOptions("digits", 2)
pander(lmEarn, style = "rmarkdown")
```

### BTW: 16.1.4.

*To determine the optimality of each group’s decisions, we will perform two-sided one-sample t-tests (with mu being the optimal proporion of acceptances--either 0 or 1) to see if the proportion of acceptances for each time/reward combination was significantly different from the optimal rate (see 11.2.). This will result in 36 independent tests (3 rewards amounts, 3 handling/travel time combinations, and 4 groups), so we will correct for multiple comparisons using False Discovery Rate (FDR).*

``` {r BTW: 16.1.4., echo=FALSE}
# in order
# clean data, 
# calculate each individual's prop. accept,
# calculate t.tests with optimality as null mean,
# correct pvalues with FDR
temp <- dataBtw %>%
  filter(Choice < 2) %>%
  group_by(SubjID, Handling, Offer, Cost) %>%
  summarise(pAccept = mean(Choice)) %>%
  mutate(optimal = case_when(
          (Handling == 10 & Offer < 8) ~ 0,
          (Handling == 14 & Offer < 20) ~ 0,
          TRUE ~ 1
        )) %>% 
  group_by(Handling, Offer, Cost) %>%
  summarise(meanAccept = mean(pAccept),
            sdAccept = sd(pAccept),
            optimal = unique(optimal),
            pvals = tryCatch(t.test(pAccept, mu = unique(optimal))$p.value, error = function(e) {1})) %>%
  mutate(FDR = p.adjust(pvals, method = "BY"),
         significant = FDR < 0.05)

# proportion of significant ones
# eventually find a way to plot this
splitData_prop <- mean(temp$significant, na.rm = T)
```

Of the 36 tests, around `r splitData_prop` were significantly deviant from optimality. Most of these were from effortful groups, as the wait group just showed deviations for 2 seconds handling/4 cent, and 10 seconds handling/8 cent offers (note to self: think about a way to properly visualize these).

CONCLUDING: these results suggest that participants were adequately influenced by the rewarding statistics of the environment, even though they did not always perform optimally.

@@

### BTW: 16.2.1.

*To compare preferences (hypothesis 4.2.), we will first perform a one-way ANOVA on the proportion of trials accepted using group as a factor. In addition, we will do pairwise comparisons on the proportion completed among all 4 groups using non-parametric permutation contrasts (6 tests). The same approach will be used for total earnings. This will give us an initial glimpse on the potential differences in cost among conditions.*

``` {r BTW: 16.2.1. Overall Proportion/Earnings, fig.align = "center", fig.width = 8, fig.height = 4, echo = FALSE}  
## ECDF of proportion completed per cost type
temp <- dataBtw %>%
        filter(Choice < 2) %>%
        mutate(Cost = factor(Cost, levels = list("Physical", "Cognitive", "Wait", "Easy"))) %>%
        group_by(SubjID, Cost) %>%
        summarise(Earnings = sum(Offer[rawChoice == 1] / 100),
                  pAccept = mean(Choice))

## formal testing 
# proportion completed
propAov <- aov(pAccept ~ factor(Cost), data = temp)

propTests <- temp %>% 
  plyr::dlply("Cost", identity) %>%
  sapply("[[", "pAccept") %>%
  as.data.frame() %>%
  combn(2, simplify = F) %>%
  sapply(function(x) {
    c(contrast = paste(colnames(x), collapse = "vs"), 
      permPval = round(permute(x[, 1], x[, 2], simple = T), digits = 3),
      cohenD = round(cohenD(x[, 1], x[, 2]), digits = 3))
  }) %>% 
  t()

@@

# earnings
earnAov <- aov(Earnings ~ factor(Cost), data = temp)

earnTests <- temp %>% 
  plyr::dlply("Cost", identity) %>%
  sapply("[[", "Earnings") %>%
  as.data.frame() %>%
  combn(2, simplify = F) %>%
  sapply(function(x) {
    c(contrast = paste(colnames(x), collapse = "vs"), 
      permPval = round(permute(x[, 1], x[, 2], simple = T), digits = 3),
      cohenD = round(cohenD(x[, 1], x[, 2]), digits = 3))
  }) %>% 
  t()

## plots
# ECDF pAcceptd
p1 <- ggplot(aes(pAccept, color = Cost), data = temp) +
        stat_ecdf(lwd = 1.2, show.legend = F) +
        scale_color_manual(values = colsBtw) +
        xlim(0, 1) +
        labs(y="ECDF", x = "Proportion Accepted") +
        theme(panel.grid.major = element_blank(), 
              panel.grid.minor = element_blank(), 
              panel.background = element_blank(), 
              axis.line = element_line(colour = "black"),
              text = element_text(size = 16))

# pAccepted
p2 <- ggplot(temp, aes(Cost, pAccept, fill = Cost)) + 
        geom_boxplot(show.legend = F) +
        scale_fill_manual(values = colsBtw) +
        ylim(c(0, 1)) +
        labs(y = "Proportion Accepted") +
        theme(panel.grid.major = element_blank(), 
            panel.grid.minor = element_blank(), 
            panel.background = element_blank(), 
            axis.line = element_line(colour = "black"),
            text = element_text(size = 16))

# earnings
p3 <- ggplot(temp, aes(Cost, Earnings, fill = Cost)) + 
        geom_boxplot(show.legend = F) +
        scale_fill_manual(values = colsBtw) +
        labs(y = "Total Earnings (dollars)") +
        theme(panel.grid.major = element_blank(), 
            panel.grid.minor = element_blank(), 
            panel.background = element_blank(), 
            axis.line = element_line(colour = "black"),
            text = element_text(size = 16))

grid.arrange(p2, p3, ncol = 2)
```

The plots show that subjects in the wait condition accepted the least and earned the most, suggesting a more optimal pattern of choices. Participants in the cognitive effort and easy conditions had higher more variable acceptance patterns, which are reflected in the comparatively low earnings. The reason why the easy condition does not show variable earnings like the cognitive effort group is probably due to the quadratic relationship between earnings and acceptances shown before.

### BTW: 16.2.2.

*In order to further look at the effect of delay, work, and rewards, we will perform a repeated measures ANOVA on the proportion completed for each combination of factors. Offer and handling time will be within-subject factors, and condition a between-subjects factor. In support of hypotheses 4.1. and 4.2., we anticipate significant main effects of handling time, reward, and cost condition, but no interactions.*

``` {r BTW: 16.2.2. rmANOVA, echo=FALSE,fig.align="center",fig.width=5,fig.height=4, results = 'asis'}
temp <- dataBtw %>%
        filter(Choice < 2) %>%
        group_by(SubjID, Cost, Handling, Offer) %>%
        summarise(pAccept = mean(Choice))

## REPEATED MEASURES ANOVA
# I think I like this the most
prop.aov <- with(temp, aov(pAccept ~ factor(Cost) * Handling * Offer + 
                                 Error(SubjID / (Handling * Offer))))

## NOTES ON RESULTS
# According to the logistic fit, there are main effects for all predictors, but no interactions. It also says that the overall odds for the wait group to accept versus the effort is around 16%. Similarly, increasing the handling time results in a decrease in the multiplicative odds of ~25%. Increments in reward increase the odds of acceptance by ~40%.
```

The plot below shows the mean proportion of acceptances (± SEM) per combination of handling time, reward, and condition (optimal acceptance rate indicated by the gray triangles). Visually, the graph confirms a couple of important intuitions. First, as the handling time increases, the proportion of acceptances decreases. Second, this discounting did not affect the 20 cent offers, as is expected from the present foraging environment. Lastly, and similar to the previous point, as the value of the offers increases so does the willingness to accept a trial. Beyond these general features, it is clear that the cognitive effort group accepted more than the other groups, regardless of the combination of experimental parameters. Notably, the optimality of this greater acceptance rate is determined by the timing context (e.g. optimal at 2 second handling time, but detrimental at 14 seconds).

>>>>

# this helps clean p-values for inclusion in text
# it takes the value, and reports < 0.001 if needed, or rounds to the second digit otherwise
report_p <- function(pval) {
  # make sure the p-values entered are numeric (sometimes they can be characters..thanks R)
  pval <- as.numeric(pval)

  # do p < 0.001 or round depending on the value
  adapted_p <- ifelse(pval < 0.001, "< 0.001", paste("=", round(pval, digits = 2)))

  print(adapted_p)
}
```

@@

- I guess you can mention that the wait group acts as a baseline of foraging behavior.
- Re-read Mikey's effort value paper to see if there is anything there that can allow us to transition into foraging. Like, are there elements that make cog effort valuable that are well encapsuled by foraging paradigms?

@@

@@

  where R, H, and P are the reward, handling time, and acceptance probability of trial i, respectively, and T is the travel times. This gave us the total reward per second attainable in each block as a function of the lowest amount accepted (i.e. acceptance threshold). Figure X shows possible earnings for each choice strategy, as well as the lowest amount participants should accept in order to maximize their rewards (circled dots). For example, a participant in a 10 s handling block should accept 8-cent and 20-cent rewards (and reject 4-cent rewards) to maximize their reward rate. Note that accepting every offer was often detrimental to participant earnings. Significant deviations from the optimal strategy can be understood as reflecting changes in subjective OC. Beyond comparing among cost types, this approach allowed us to test if certain demands boosted the value of offers (i.e. over-accepting low offers).

@@

	Our foraging task was configured such that over and under accepting were detrimental to total earnings. To confirm this, we fit a general linear model with constant, linear, and quadratic terms to estimate the correspondence between proportion accepted (independent variable) and total earnings (dependent variable). A significant quadratic coefficient thus would signal that the task statistics operated as expected. Next, to determine the optimality of each group’s decisions, performed two-sided one-sample t-tests to see if the proportion of acceptances for each time/reward combination was significantly different from the optimal rate (see Operationalization of Cost above). This resulted in 36 independent tests (3 rewards amounts, 3 handling/travel time combinations, and 4 groups), so we corrected for multiple comparisons using False Discovery Rate (FDR) **CHANGE TO COST3 APPROACH.**
  Next, we compared preferences among cost conditions. We first performed a one-way ANOVA on the proportion of trials accepted using group as a factor. We then compared the proportion completed among all 4 groups using non-parametric permutation contrasts (6 tests). The same approach was used for total earnings. This gave us an initial glimpse on the potential differences in cost among conditions. In order to further look at the effect of handling, offer, and cost type, we computed the probability of accepting a trial with a mixed-effects logistic regression using the lme4 package (CITE). Based on the task structure and our main question, our a priori model of interest included cost condition, handling time, and reward amount as fixed main effects, and participant ID as a random effect. Cost condition was modeled with three categorical terms, with the fourth condition as the reference condition. We ran three versions of the model with different reference conditions, in order to test all pairwise differences among the four cost conditions. As preregistered, we anticipated significant main effects (coefficients different than zero) of handling time, reward, and cost condition. In addition, we hypothesized that the probability of accepting would be significantly great in either effort condition compared to wait and easy groups. We then examined whether this a priori model outperformed both simpler and more complex models. We used both Akaike’s Information Criterion (AIC) and Bayesian Information Criterion (BIC) to determine the model that minimized the negative log-likelihood while penalizing the addition of parameters. The regression with each combination of predictors was fitted in the following order: 1) intercept only; 2) cost type only; 3) handling time only; 4) reward only; 5) condition, handling, and reward main effects (a priori model); 6) adding a handling-by-reward interaction; and 7) adding all three possible two-way interactions. We predicted that model 5 would have the lowest AIC.

@@

  To compare acceptance rates among cost conditions, we first computed the probability of accepting a trial with a mixed-effects logistic regression. The model included cost condition and reward amount as fixed main effects, and subject ID as a random effect. Cost condition was modeled with three categorical terms, with the fourth condition as the reference condition (two effort conditions, and two delay conditions corresponding to each effort type). We ran three versions of the model with different reference conditions, in order to test all relevant pairwise differences among the four cost conditions. Next, we compared this model to both simpler and more complex models using Akaike’s Information Criterion (AIC) and Bayesian Information Criterion (BIC). We added varied model complexity in the following order: 1) intercept only; 2) condition only; 3) handling time only; 4) offer amount only; 5) handling time and offer amount (added to the preregistered comparison); 6) condition, handling time, and reward main effects (a priori model from above); 7) adding a handling-by-reward interaction; and 8) all possible two-way interactions. We predicted that model 6 would have the last considerable decrease in the negative log-likelihood. Nested models with similar AIC were statistically compared using an analysis-of-deviance. The significance test was computed as the probability of the reduction in deviance, based on a chi-square distribution with degrees of freedom equal to the difference in the number of parameters between models.

@@

``` {r BTW: 16.1.1. Individual logistic, fig.align="center", fig.width = 4, fig.height = 4, echo = FALSE}
# filter out errors and compute R + H logistic per subject, then get coefficients
logisRH <- dataBtw %>%
  filter(Choice < 2) %>%
  plyr::dlply("SubjID", identity) %>%
  lapply(function(data) {glm(Choice ~ Handling + Offer, data = data, family = "binomial")}) %>%
  sapply(coefficients)

@@

# Plot coeffs
temp <- melt(logisRH[c("Handling", "Offer"), ])
plot_handoffer <- qplot(data = temp, x = Var1, y = value, geom = "boxplot") + 
                    labs(x = "", y = "Coefficients") +
                    geom_hline(yintercept = 0, linetype = "dashed") +
                    theme(legend.position = c(0.9, 0.7),
                         panel.grid.major = element_blank(), 
                         panel.grid.minor = element_blank(), 
                         panel.background = element_blank(), 
                         axis.line = element_line(colour = "black"),
                         text = element_text(size = 16))
```

``` {r BTW: 16.1.2. AR, echo = FALSE, include = FALSE}
# Idea: do AIC to compare models per participant
# add an AR regressor to track recent quits
logisRHAR <- dataBtw %>%
              filter(Choice < 2) %>%
              group_by(SubjID) %>%
              mutate(AR = seqQuits(Choice)) %>%
              plyr::dlply("SubjID", identity) %>%
              lapply(function(data) {suppressWarnings(glm(Choice ~ Handling + Offer + AR, data = data, family = "binomial"))})

@@

@@

# plot
# (earnFitplot <- ggplot(data = temp, aes(pComplete, Earnings)) + 
#          scale_color_manual(values = colsBtw) + 
#          geom_point(aes(fill = Cost), pch = 21, color = "black", size = 3, show.legend = T) + 
#          stat_smooth(aes(y = Earnings), method = "lm", formula = y ~ x + I(x^2), color = "grey30") +
#          labs(x = "Proportion Completed", y = "Total Earnings (dollars)") +
#          scale_fill_manual(values = colsBtw) +
#          theme(panel.grid.major = element_blank(), 
#            panel.grid.minor = element_blank(), 
#            panel.background = element_blank(), 
#            axis.line = element_line(colour = "black"),
#            text = element_text(size = 16)))

# Summary table for the linear model
# panderOptions("digits", 2)
# pander(lmEarn, style = "rmarkdown")

@@

``` {r BTW: 16.1.4. Optimality (move to acceptance comparison eventually), echo = FALSE}
# in order
# clean data, 
# calculate each individual's prop. accept,
# calculate t.tests with optimality as null mean,
# correct pvalues with FDR
temp <- dataBtw %>%
  filter(Choice < 2) %>%
  group_by(SubjID, Handling, Offer, Cost) %>%
  summarise(pAccept = mean(Choice)) %>%
  mutate(optimal = case_when(
          (Handling == 10 & Offer < 8) ~ 0,
          (Handling == 14 & Offer < 20) ~ 0,
          TRUE ~ 1
        )) %>% 
  group_by(Handling, Offer, Cost) %>%
  summarise(meanAccept = mean(pAccept),
            sdAccept = sd(pAccept),
            optimal = unique(optimal),
            pvals = tryCatch(t.test(pAccept, mu = unique(optimal))$p.value, error = function(e) {1})) %>%
  mutate(FDR = p.adjust(pvals, method = "BY"),
         significant = FDR < 0.05)

# proportion of significant ones
# eventually find a way to plot this (or just place it further down)
# alternative per block: temp %>% group_by(Handling) %>% summarise(prop = mean(significant, na.rm = T))
optimalProp <- mean(temp$significant, na.rm = T) * 100

# proportion accepted per cost condition
optimalProp_cost <- temp %>% 
  group_by(Cost) %>% 
  summarise(propDeviations = round(mean(significant) * 100))

# # potential visualization, though difficult to interpret
# temp %>% 
#   filter(Cost != "Easy") %>%
#   select(Handling, Cost, Offer, significant) %>%
#   ggplot(aes(Cost, interaction(Offer, Handling), fill = significant)) +
#   geom_tile(color = "white") +
#   theme_minimal()
```

  In this experiment, groups faced with different behavioral costs (physical effort, cognitive effort, or delay) were tasked with deciding their preferred strategy to maximize rewards in fully-disclosed foraging environments of variable richness. Environmental richness was dictated by the time it took to obtain a reward (the handling time) and the time between trials (the travel time). We hypothesized that participants would approximate reward-maximizing behavior by preferring higher rewards and shorter delays, but that changing the cost required to obtain rewards would uniformly increase or decrease this choice pattern. Specifically, we predicted that participants confronted with cognitive demands would be more likely to accept trials than those faced with physical effort and delay, regardless of handling time and reward amount.
  To address the first hypothesis, we first confirmed that increasing handling times and reward amounts produced the expected reduction and increase in acceptance probabilities, respectively. Since participants in the effort groups were forced to travel when they failed to perform above threshold (see Methods), we distinguish between acceptances (entering the handling period) and completions (successfully obtaining a reward). Individual-specific logistic regression coefficients for handling time were significantly lower than 0 (mean $\beta$ = `r mean(coeffRH_mean[2], na.rm = T)`, SE = `r coeffRH_se[2]`; Wilcoxon test: V = `r rankHand$statistic`, *p* `r report_p(rankHand$p.value)`), whereas increasing the reward amount resulted in higher acceptance probabilities (mean $\beta$ = `r coeffRH_mean[1]`, SE = `r coeffRH_se[1]`; Wilcoxon test: V = `r rankOffer$statistic`, p `r report_p(rankOffer$p.value)`). We next examined whether choices could also have been affected by recent choice history (i.e. if too many sequential quits promoted acceptances regardless of reward amount) by adding a regressor to the model that tracked the number of consecutive quits preceding a trial. This auto-regressive coefficient was not significantly different than 0 (mean $\beta$ = `r coeffRHAR_mean[3]`, SE = `r coeffRHAR_se[3]`; Wilcoxon test: V = `r rankRHAR$statistic`, p `r ifelse(rankRHAR$p.value < 0.001, "< 0.001", paste("=", round(rankRHAR$p.value, digits = 2)))`), and the 95% confidence interval (CI) of these coefficients contained 0 in `r round((sum(AR_CIs) / nSubjs_btw) * 100)`% of our participants. This indicates that offer patterns did not influence participant behavior.
  **Maybe put this as an addendum to the mixed effects analysis of proportion of acceptances, after mixed models** . The foraging task was configured so that there was an optimal, reward-maximizing strategy (see Operationalization of Cost in Methods). Because of this, participants were told to consider their strategies carefully, as accepting everything would not maximize their gains. Figure X shows that participants who over- or under-accepted earned the least (general linear model with quadratic term, F = `r round(summary(lmEarn)$fstatistic[1], digits = 2)`, Beta = `r summary(lmEarn)$coefficients[3,1]`, SE = `r round(summary(lmEarn)$coefficients[3, 2], digits = 2)`, R-squared = `r round(summary(lmEarn)$r.squared, digits = 2)`). Two-sided, one-sample t-tests against the optimal proportion of acceptances (i.e. $\mu$ = 0 or 1) for each combination of cost type, handling time, and offer showed that participants significantly deviated from optimality in `r round(optimalProp)` of combinations (*p* < 0.05, FDR corrected), with the proportion of deviations being lowest for the wait group (Wait = `r filter(optimalProp_cost, Cost == "Wait")[2]`, physical = `r filter(optimalProp_cost, Cost == "Physical")[2]`, Cognitive = `r filter(optimalProp_cost, Cost == "Cognitive")[2]`, Easy = `r filter(optimalProp_cost, Cost == "Easy")[2]`). Together, these results suggest that participants were adequately influenced by the rewarding statistics of the environment, even though they did not always perform optimally.

@@

``` {r BTW: 16.2.1. Overall Proportion/Earnings, fig.align = "center", fig.width = 8, fig.height = 4, echo = FALSE}  
## earnings and proportion accepted per cost type
# note that earnings are based on successful completions, not just acceptances
temp <- dataBtw %>%
        group_by(SubjID, Cost) %>%
        summarise(Earnings = sum(Offer[(Choice == 1) & (rawChoice < 2)] / 100),
                  pAccept = mean(Choice))

## summaries
overallSumms <- temp %>% 
  group_by(Cost) %>% 
  summarise (mProp = mean(pAccept), 
             sdProp = sd(pAccept), 
             mEarn = mean(Earnings), 
             sdEarn = sd(Earnings)) %>%
  mutate_if(is.numeric, round, digits = 2)

## formal testing 
# proportion completed
propAov <- summary(aov(pAccept ~ Cost, data = temp))

propTests <- temp %>% 
  plyr::dlply("Cost", identity) %>%
  sapply("[[", "pAccept") %>%
  as.data.frame() %>%
  combn(2, simplify = F) %>%
  sapply(function(x) {
    c(contrast = paste(colnames(x), collapse = ifelse(cohenD(x[, 1], x[, 2]) < 0, " < ", " > ")), 
      permPval = round(permute(x[, 1], x[, 2], simple = T), digits = 3),
      cohenD = abs(round(cohenD(x[, 1], x[, 2]), digits = 3)))
  }) %>% 
  t() %>%
  as_tibble()

@@

# earnings 
earnAov <- summary(aov(Earnings ~ Cost, data = temp))

earnTests <- temp %>% 
  plyr::dlply("Cost", identity) %>%
  sapply("[[", "Earnings") %>%
  as.data.frame() %>%
  combn(2, simplify = F) %>%
  sapply(function(x) {
    c(contrast = paste(colnames(x), collapse = ifelse(cohenD(x[, 1], x[, 2]) < 0, " < ", " > ")), 
      permPval = round(permute(x[, 1], x[, 2], simple = T), digits = 3),
      cohenD = abs(round(cohenD(x[, 1], x[, 2]), digits = 3)))
  }) %>% 
  t() %>%
  as_tibble()

## plots
# pAccepted
p1 <- ggplot(temp, aes(Cost, pAccept, fill = Cost)) + 
        geom_boxplot(show.legend = F) +
        scale_fill_manual(values = colsBtw) +
        ylim(c(0, 1)) +
        labs(y = "Proportion Accepted") +
        theme(panel.grid.major = element_blank(), 
            panel.grid.minor = element_blank(), 
            panel.background = element_blank(), 
            axis.line = element_line(colour = "black"),
            text = element_text(size = 16))

# earnings
p2 <- ggplot(temp, aes(Cost, Earnings, fill = Cost)) + 
        geom_boxplot(show.legend = F) +
        scale_fill_manual(values = colsBtw) +
        labs(y = "Total Earnings (dollars)") +
        theme(panel.grid.major = element_blank(), 
            panel.grid.minor = element_blank(), 
            panel.background = element_blank(), 
            axis.line = element_line(colour = "black"),
            text = element_text(size = 16))

grid.arrange(p1, p2, ncol = 2)
```

  The next set of analyses examined the hypothesis that choice differences among costs would be characterized by more acceptances by the cognitive group **not quite**. Figure X shows that the cognitive effort group consistently accepted more offers, which resulted in lower earnings. One-way ANOVAs showed that differences among groups were significant both for overall acceptance rates (F = `r round(propAov[[1]][1, 4], digits = 2)`, *p* `r report_p(propAov[[1]][1, 5])`), and total earnings (F = `r round(earnAov[[1]][1, 4], digits = 2)`, *p* `r report_p(earnAov[[1]][1, 5])`). We then performed post-hoc permutations (5000 iterations) comparing mean acceptance rates between every pair of costs. On each iteration the group assignment was randomly shuffled without replacement, and the difference in mean acceptance rates across iterations created a putative null distribution. The unpermuted group mean difference was then evaluated against this permuted distribution. This analysis confirmed that acceptance rates of the cognitive effort group (mean = `r filter(overallSumms, Cost == "Cognitive") %>% select(mProp)`, SD = `r filter(overallSumms, Cost == "Cognitive") %>% select(sdProp)`) were higher than those of the physical (mean = `r filter(overallSumms, Cost == "Physical") %>% select(mProp)`, SD = `r filter(overallSumms, Cost == "Physical") %>% select(sdProp)`; permuted *p* = `r report_p(filter(propTests, contrast == "Physical < Cognitive") %>% select(permPval))`, Cohen's D = `r filter(propTests, contrast == "Physical < Cognitive") %>% select(cohenD)`) and wait groups (mean = `r filter(overallSumms, Cost == "Wait") %>% select(mProp)`, SD = `r filter(overallSumms, Cost == "Wait") %>% select(sdProp)`; permuted *p* = `r report_p(filter(propTests, contrast == "Cognitive > Wait") %>% select(permPval))`, Cohen's D = `r filter(propTests, contrast == "Cognitive > Wait") %>% select(cohenD)`). It also showed that those faced with the easy task accepted more than those in the wait group, although responses from the easy group were more variable (mean Easy = `r filter(overallSumms, Cost == "Easy") %>% select(mProp)`, SD = `r filter(overallSumms, Cost == "Easy") %>% select(sdProp)`; permuted *p* = `r report_p(filter(propTests, contrast == "Wait < Easy") %>% select(permPval))`, Cohen's D = `r filter(propTests, contrast == "Wait < Easy") %>% select(cohenD)` (all other *p* > 0.05). 
  We repeated these pairwise permutation to identify differences in earnings. In line with the earnings results from the previous section (see Figure X), the additional acceptances produced by the cognitive effort group resulted in significantly lower earnings (mean = `r filter(overallSumms, Cost == "Cognitive") %>% select(mEarn)`, SD = `r filter(overallSumms, Cost == "Cognitive") %>% select(sdEarn)`) than both physical (mean = `r filter(overallSumms, Cost == "Physical") %>% select(mEarn)`, SD = `r filter(overallSumms, Cost == "Physical") %>% select(sdEarn)`; permuted *p* = `r report_p(filter(earnTests, contrast == "Physical > Cognitive") %>% select(permPval))`, Cohen's D = `r filter(earnTests, contrast == "Physical > Cognitive") %>% select(cohenD)`) and wait groups (mean = `r filter(overallSumms, Cost == "Wait") %>% select(mEarn)`, SD = `r filter(overallSumms, Cost == "Wait") %>% select(sdEarn)`; permuted *p* = `r report_p(filter(earnTests, contrast == "Cognitive < Wait") %>% select(permPval))`, Cohen's D = `r filter(earnTests, contrast == "Cognitive < Wait") %>% select(cohenD)`). In addition, we found that the wait group earned more than the physical (permuted *p* = `r report_p(filter(earnTests, contrast == "Physical < Wait") %>% select(permPval))`, Cohen's D = `r filter(earnTests, contrast == "Physical < Wait") %>% select(cohenD)`) and easy groups (mean Easy = `r filter(overallSumms, Cost == "Easy") %>% select(mEarn)`, SD = `r filter(overallSumms, Cost == "Easy") %>% select(sdEarn)`; permuted *p* = `r report_p(filter(earnTests, contrast == "Wait > Easy") %>% select(permPval))`, Cohen's D = `r filter(earnTests, contrast == "Wait > Easy") %>% select(cohenD)`).
  These findings provide a first glimpe at differences in cost, showing that individuals in the wait condition accepted the least and earned the most. Moreover, they suggest that cognitive demands can boost the value of an offer instead, even when accepting it negatively impacts total earnings.
